Adopting agile in the large: motivations, success factors and challenges

### 2014-04-22 journal/article.tex
Reasons to change table

>>>>

As stated by Research Question 1 we investigated the reasons organizations start
a transformation process towards agile software development. In most primary
reasons for starting the transformation were mentioned, and only 7 cases of 42
did not mention any reasons. In the cases giving no specific reason to change it
was simply mentioned that management had decided to change the organization.
The reasons for organizations to change that were found are presented in table
\ref{table:reasonstochange}. The reasons to change were mainly demands for
improvement or identified problems in the current process.

Some cases reported that the organization had been successful in waterfall
delivery for a long time before the agile transformation.

\begin{table}
    \begin{tabular}{ p{1.5cm} l l }
        \toprule
        Reason    &  Examples  &  Sources   \\
        \midrule

        \multicolumn{3}{l}{Demand of improved delivery speed or frequency}  \\
         &  Time To Market must lessen           & x \\
         &  Demand for frequent deliveries       & x \\
         &  Too long cycle time before feedback  & x \\

        \multicolumn{3}{l}{General problems with management of software development} \\
         &  General management dysfunction                & x \\
         &  Problems with motivation and morale           & x \\
         &  Problems coordinating a growing organization  & x \\

        \multicolumn{3}{l}{Demand for flexibility or responsiveness}  \\
         &  Responsiveness to business needs  & x \\
         &  Adaptation as projects evolve     & x \\

        \multicolumn{3}{l}{Problems with overhead and excess in process}  \\
         &  Excess, slowness and costs caused by process  & x \\
         &  The current process is being ignored          & x \\

        \multicolumn{3}{l}{Demand to improve product quality}  \\

        \multicolumn{3}{l}{Problems with planning or keeping schedules}  \\

        \multicolumn{3}{l}{Demand of better customer collaboration}  \\
         &  Customers push for improvement  & x \\

        \multicolumn{3}{l}{Lack of focus or priorities}  \\
         &  Business needs or priorities are not regarded  & x \\
         &  Requirements are not understood                & x \\

        \multicolumn{3}{l}{Communication and collaboration dificulties}  \\
         &  Communication difficulties across and within projects  & x \\
         &  Teams work in silos or isolation  & x \\

        \bottomrule
    \end{tabular}
    \caption{Summarizing why large organizations initiate an agile transformation (RQ1)}
    \label{table:reasonstochange}
\end{table}
